Eye-tracking on the web: lessons learned from replicating 5 experiments

### 2022-04-21 manuscript.Rmd
minor reknit manuscript

<!-- MAJOR TO DOs: 
 - get data from in-lab versions of group A (AJ) and group D (RR)
 - replicate group D and A in lab

 (see bottom for notes from e-mails)
 -->

Intro stuff:

@@

_Present work_

@@

## Eye-tracking Calibration and Validation
<!--took paragraph below from group D's methods -->
When participants began the experiment, they were notified the webcam would be used for eye tracking but no video would be saved. They were asked to remove glasses if possible, close any other tabs or apps, turn off notifications, and make sure their face was lit from the front. The webcam’s view of the participant popped up on the screen, and participants were asked to center their face in the box and keep their head still. The experiment window then expanded to full screen, and participants began the eye-tracking calibration.

@@

## Data pre-processing
We used `r cite_r("references.bib")` for all our analyses.

# Experiment 1
<!-- group a -->

The first study was a replication attempt of @altmannIncrementalInterpretationVerbs1999. Altmann and Kamide used the visual world eye-tracking paradigm [@tanenhaus1995] to show that meanings of verbs rapidly constrain the set of potential subsequent referents in sentence processing. For example, when looking at the display in Figure XX and listening to a sentence like “The boy will eat the…,” participants are more likely to look at the cake than when they hear “The boy will move the…,” in which case they tend to look at the train, presumably because cakes are edible and trains are not. Semantic information available at the verb is used to anticipate upcoming linguistic input.

@@

## Methods
<!-- since there are not the analysis scripts we're using, I'm not sure about the best way to link to this -->
All stimuli, experiment scrips, data, analysis scripts, and pre-registration are available on the Open Science Framework at [https://osf.io/s82kz](https://osf.io/s82kz).

@@

60 participants were paid $XX for their participation. Our sample size of participants was determined by the total run time of our experiment, ~10 minutes, and the allotted funding from the Vassar College Cognitive Science Department. From this information, we calculated a reasonable number of participants we could afford to compensate on Prolific. Note that the sample size of the original study was 24. For unknown reasons, 2 of the subjects’ results were not recorded, so in the analysis, we worked with data collected from 58 participants.

@@

The task began with an <number of points>-point eye-tracker calibration and validation. During the experiment, the participants were simultaneously presented with a visual image and a corresponding audio recording of a spoken sentence. Participants had to input a keyboard response indicating “yes” or “no” as to whether the sentence they heard was feasible given the visual image. There were two practice trials to ensure that participants had a sound understanding of the instructions before they undertook the main portion of the experiment. Participants’ reaction times, keyboard responses, and looks to objects in the scene were recorded for each trial.

<!-- Qs: 
-keyboard keys? what was the exact phrasing of the instruction? 
-Any delay between when visual scene appears and the audio starts? 
-Does trial end as soon as participant responds?-->

### Materials & Design

@@

* here we will describe the analyses that are as close as possible to the original paper with a minimal validation cutoff

* same analysis but with stricter validation cutoff

@@

* here we will describe a direct comparison to data collected in the lab

@@

* here we will describe the analyses that correlate calibration quality with effect size at the individual level

@@

# Experiment 2
<!-- group b -->

@@

60 participants were paid $XX for their participation <!--right?-->. The sample size was motivated in part by budget constraints, but was nonetheless 2.5x larger than the original sample size of 24, as suggested by Simonsohn (2015). Data from 1 participant were not properly recorded due to unknown technical issues, so data from 59 participants were included in all analyses to follow.

@@

During the recall phase, participants listened to statements and responded by pressing the ‘F’ key for false statements and ‘T’ for true ones. Each statement fell into either an interobject or intraobject condition. Interobject statements were those that compared two different items in the grid (e.g. “The skeleton is to the left of the robot”), while intraobject statements were those that asked about the orientation of a single item (e.g. “The bus is facing right”). There were 48 total statements, with 24 interobject and 24 intraobject statements split evenly among the four quadrants. While listening to these statements, in the free-viewing block, participants saw a blank screen and were allowed to freely gaze around the screen. During the fixed-viewing block, participants were asked to fixate a small cross in the center of the screen throughout the recall phase. In both cases, the mouse was obscured from the screen. Participants were randomly assigned to see the fixed-viewing or free-viewing block first.

@@

The primary methodological difference between this replication and Johansson and Johansson’s study was that the original study included two additional viewing conditions that were omitted from this replication due to time constraints. In those two conditions, participant were prompted to look to a specific quadrant (rather than free viewing or central fixation) which either matched or mismatched the original location of the to-be-remembered item.

@@

# Experiment 3
<!-- group c -->

@@

 Approximately 24 hours after completing the first session, with a leeway interval of 12 hours to accommodate busy schedules, participants were given the recognition test. It consisted of 48 photographs, presented one at a time. Each was shown on the screen for 1 second, followed by a 1 second interstimulus interval. Half of the pohotographs had been viewed twice on the previous day and were deemed the “targets.” The other half depicted an object with the same name as an object in one of the old photographs, but had not been viewed before, deemed “foils.” Each photograph remained on the screen until the participants indicated whether or not they had seen it before by pressing ‘y’ for yes and ‘n’ for no. After they pressed one of the two keys, a prompt on the screen asked them to rate their confidence in their answer from 1 as a “pure guess” to 5 as “very sure.” by clicking on the corresponding number on the screen. No feedback on their responses was given during the test.

@@

There were two modifications we made to the methods of the original experiment. As we are only replicating the declarative memory component of the original experiment, we did not have a “priming group.” Therefore, we followed only the procedure for the “looking group.” Additionally, for each section of the study, the stimuli was presented on a single screen instead of two screens due to the constraints of the online experiment format.

@@

# Experiment 4
<!-- group d -->

The fourth study was a replication attempt of Experiment 1 in @ryskinVerbBiasesAre2017, which was closely modeled on @snedekerDevelopingConstraintsParsing2004a. These studies used the visual world paradigm to show that listeners use knowledge of the co-occurrence statistics of verbs and syntactic structures to resolve ambiguity. For example, in a sentence like “Feel the frog with the feather,” the phrase “with the feather” could be describing the frog, or it could be describing the instrument that should be used to do the “feeling.” When both options (a frog holding a feather and a feather by itself) are available in the visual display, listeners rely on the verb’s “bias” (statistical co-occurrence either in norming or corpora) to rapidly choose an action while the sentence is unfolding.
.

@@

The stimuli, experimental code, and data and analysis scripts can be found on the Open Science Framework at the following link, https://osf.io/x3c49/ (https://osf.io/x3c49/). The pre-registration for the study can be found at https://osf.io/3v4pg (https://osf.io/3v4pg).

@@

58 (??) participants were paid $XX for their participation <!--right?-->. A sample size of 58 was chosen because we wanted to replicate the experiment with greater statistical power. Note that the original study had a sample size of 24.

@@

During a trial, four pictures were displayed (target animal, target instrument, distractor animal, distractor instrument), one in each corner of the screen, and participants heard an audio prompt that contained instructions about the action they needed to act out (e.g., "Rub the butterfly with the crayon"; see Figure XX)^[In the original study, the pictures appeared one by one on the screen and their names were played as they appeared. We removed this introductory portion of the trial to save time]. Using their cursor, participants could act out the instructions by clicking on objects and moving them or motioning over the objects^[ As opposed to the original study we recorded mouse movement instead of clicking behavior since not all of the audio prompts required clicking. For example, the sentence “locate the camel with the straw” may not involve any clicking but rather only mousing over the camel.]. After the action was completed, the participants were instructed to press the space bar which led to a screen that said “Click Here” in the middle in order to remove bias in the eye and mouse movements from the previous trial. The experiment only allowed the participants to move on to the next trial once the audio was completely done playing and the mouse had been moved over at least one object.

@@

The images and audios presented to the participants were the same stimuli used in the original study (available here <link>). The critical trials were divided into modifier-biased, instrument-biased, and equibiased conditions, and the filler trials did not contain ambiguous instructions. Two lists of critical trials were made with different verb and instrument combinations (e.g., “rub” could be paired with “panda” and “crayon” in one list and “panda” and “violin” in the second list). Within each list, the same verb was presented twice but each time with a different target instrument and animal. The lists were randomly assigned to the participants to make sure the effects were not caused by the properties of the animal or instrument images used. The list of verbs used can be found in Appendix A of the original study.

@@

# Experiment 5
<!-- group e -->

@@

All stimuli, experiment scripts, data, and analysis scripts are available on the Open Science Framework at https://osf.io/eubsc/ (https://osf.io/eubsc/). The study pre-registration is available at https://osf.io/tv57s (https://osf.io/tv57s).

@@

50 participants for the main task were recruited on Prolific and were paid $XX. 8 subjects, 4 from the attractiveness task group and 4 from the roundness task group, were excluded for incorrect validations. <!-- they were able to proceed despite bad validation?--> After this data exclusion, we ended up with 21 participants each for the attractiveness task and the roundness task. The original sample size in Shimojo et al. (2003) was 10 participants total. 
### Procedure and Design

@@

During each trial of the main task, two faces were displayed on the two halves of the screen, one on the left and one on the right (as in Figure XX). Participants were randomly assigned to one of two tasks: attractiveness or shape judgment. In the attractiveness task, participants were asked to chose the more attractice face in the pair and in the shape judgment task participants were asked to pick the face that appeared rounder. They pressed the "a" key on their keyboard to select the face on the left and the “d” key to select the face on the right. A fixation cross appeared in the center of the screen between each set of faces. Participants were asked to look at this fixation cross in order to reset their gaze in between trials (???). The order of the 19 face pairs was random for each participant.

@@

The faces in our replication were selected from a set of 1,000 faces within the Flickr-Faces-HQ Dataset. (The face images used in Shimojo et al. were from the Ekman face database and the AR face database.) These images were chosen because the person in each image was looking at the camera with a fairly neutral facial expression and appeared to be over the age of 18. 27 participants were recruited on Prolific to participate in stimulus norming (for attractiveness). They were paid $XX for completing the experiment. Data from 3 participants was excluded because their mode response made up more than 50% of their total responses <!-- is this a cutoff from Shimojo?-->, for a total of 24 participants in the norming. They each viewed all 172 faces and were asked to rate them on a scale from 1 (less attractive) to 7 (more attractive) using a slider. Faces were presented one at a time and in a random order for each participant. Following Shimojo et al., 19 face pairs were made by matching two faces that had a difference in mean attractiveness ratings that was 0.25 points or lower and that matched in gender, race, and age group (young adult, adult, or older adult).

@@

<!-- posner cueing task
# Experiment 6

@@

## Discussion
 -->

# Combined Analyses

@@

<!-- NOTES FROM EMAILS:

@@

We also included a step where if the validation was poor after the first attempt we repeated the calibration and validation procedure one additional time. So some subjects have more validation trials than others. If you look at my R Notebook for group A (just pushed to GH now) you can see some initial attempts to extract validation info and use it to exclude subjects. -->

\newpage

@@

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

>>>>

```{=html}
<!-- MAJOR TO DOs: 
 - get data from in-lab versions of group A (AJ) and group D (RR)
 - replicate group D and A in lab

 (see bottom for notes from e-mails)
 -->
```
Intro stuff:

@@

*Present work*

@@

## Eye-tracking Calibration and Validation

<!--took paragraph below from group D's methods -->

When participants began the experiment, they were notified the webcam
would be used for eye tracking but no video would be saved. They were
asked to remove glasses if possible, close any other tabs or apps, turn
off notifications, and make sure their face was lit from the front. The
webcam's view of the participant popped up on the screen, and
participants were asked to center their face in the box and keep their
head still. The experiment window then expanded to full screen, and
participants began the eye-tracking calibration.

@@

## Data pre-processing

We used `r cite_r("references.bib")` for all our analyses.

# Experiment 1

<!-- group a -->

The first study was a replication attempt of
@altmannIncrementalInterpretationVerbs1999. Altmann and Kamide used the
visual world eye-tracking paradigm [@tanenhaus1995] to show that
meanings of verbs rapidly constrain the set of potential subsequent
referents in sentence processing. For example, when looking at the
display in Figure XX and listening to a sentence like "The boy will eat
the...," participants are more likely to look at the cake than when they
hear "The boy will move the...," in which case they tend to look at the
train, presumably because cakes are edible and trains are not. Semantic
information available at the verb is used to anticipate upcoming
linguistic input.

@@

<!-- since there are not the analysis scripts we're using, I'm not sure about the best way to link to this -->

All stimuli, experiment scrips, data, analysis scripts, and
pre-registration are available on the Open Science Framework at
<https://osf.io/s82kz>.

@@

60 participants were paid \$XX for their participation. Our sample size
of participants was determined by the total run time of our experiment,
\~10 minutes, and the allotted funding from the Vassar College Cognitive
Science Department. From this information, we calculated a reasonable
number of participants we could afford to compensate on Prolific. Note
that the sample size of the original study was 24. For unknown reasons,
2 of the subjects' results were not recorded, so in the analysis, we
worked with data collected from 58 participants.

@@

The task began with an <number of points>-point eye-tracker calibration
and validation. During the experiment, the participants were
simultaneously presented with a visual image and a corresponding audio
recording of a spoken sentence. Participants had to input a keyboard
response indicating "yes" or "no" as to whether the sentence they heard
was feasible given the visual image. There were two practice trials to
ensure that participants had a sound understanding of the instructions
before they undertook the main portion of the experiment. Participants'
reaction times, keyboard responses, and looks to objects in the scene
were recorded for each trial.

```{=html}
<!-- Qs: 
-keyboard keys? what was the exact phrasing of the instruction? 
-Any delay between when visual scene appears and the audio starts? 
-Does trial end as soon as participant responds?-->
```
### Materials & Design

@@

-   here we will describe the analyses that are as close as possible to
    the original paper with a minimal validation cutoff

-   same analysis but with stricter validation cutoff

@@

-   here we will describe a direct comparison to data collected in the
    lab

@@

-   here we will describe the analyses that correlate calibration
    quality with effect size at the individual level

@@

# Experiment 2

<!-- group b -->

@@

60 participants were paid \$XX for their participation <!--right?-->.
The sample size was motivated in part by budget constraints, but was
nonetheless 2.5x larger than the original sample size of 24, as
suggested by Simonsohn (2015). Data from 1 participant were not properly
recorded due to unknown technical issues, so data from 59 participants
were included in all analyses to follow.

@@

During the recall phase, participants listened to statements and
responded by pressing the 'F' key for false statements and 'T' for true
ones. Each statement fell into either an interobject or intraobject
condition. Interobject statements were those that compared two different
items in the grid (e.g. "The skeleton is to the left of the robot"),
while intraobject statements were those that asked about the orientation
of a single item (e.g. "The bus is facing right"). There were 48 total
statements, with 24 interobject and 24 intraobject statements split
evenly among the four quadrants. While listening to these statements, in
the free-viewing block, participants saw a blank screen and were allowed
to freely gaze around the screen. During the fixed-viewing block,
participants were asked to fixate a small cross in the center of the
screen throughout the recall phase. In both cases, the mouse was
obscured from the screen. Participants were randomly assigned to see the
fixed-viewing or free-viewing block first.

@@

The primary methodological difference between this replication and
Johansson and Johansson's study was that the original study included two
additional viewing conditions that were omitted from this replication
due to time constraints. In those two conditions, participant were
prompted to look to a specific quadrant (rather than free viewing or
central fixation) which either matched or mismatched the original
location of the to-be-remembered item.

@@

# Experiment 3

<!-- group c -->

@@

Approximately 24 hours after completing the first session, with a leeway
interval of 12 hours to accommodate busy schedules, participants were
given the recognition test. It consisted of 48 photographs, presented
one at a time. Each was shown on the screen for 1 second, followed by a
1 second interstimulus interval. Half of the pohotographs had been
viewed twice on the previous day and were deemed the "targets." The
other half depicted an object with the same name as an object in one of
the old photographs, but had not been viewed before, deemed "foils."
Each photograph remained on the screen until the participants indicated
whether or not they had seen it before by pressing 'y' for yes and 'n'
for no. After they pressed one of the two keys, a prompt on the screen
asked them to rate their confidence in their answer from 1 as a "pure
guess" to 5 as "very sure." by clicking on the corresponding number on
the screen. No feedback on their responses was given during the test.

@@

There were two modifications we made to the methods of the original
experiment. As we are only replicating the declarative memory component
of the original experiment, we did not have a "priming group."
Therefore, we followed only the procedure for the "looking group."
Additionally, for each section of the study, the stimuli was presented
on a single screen instead of two screens due to the constraints of the
online experiment format.

@@

# Experiment 4

<!-- group d -->

The fourth study was a replication attempt of Experiment 1 in
@ryskinVerbBiasesAre2017, which was closely modeled on
@snedekerDevelopingConstraintsParsing2004a. These studies used the
visual world paradigm to show that listeners use knowledge of the
co-occurrence statistics of verbs and syntactic structures to resolve
ambiguity. For example, in a sentence like "Feel the frog with the
feather," the phrase "with the feather" could be describing the frog, or
it could be describing the instrument that should be used to do the
"feeling." When both options (a frog holding a feather and a feather by
itself) are available in the visual display, listeners rely on the
verb's "bias" (statistical co-occurrence either in norming or corpora)
to rapidly choose an action while the sentence is unfolding. .

@@

The stimuli, experimental code, and data and analysis scripts can be
found on the Open Science Framework at the following link,
<https://osf.io/x3c49/> (<https://osf.io/x3c49/>). The pre-registration
for the study can be found at <https://osf.io/3v4pg>
(<https://osf.io/3v4pg>).

@@

58 (??) participants were paid \$XX for their participation
<!--right?-->. A sample size of 58 was chosen because we wanted to
replicate the experiment with greater statistical power. Note that the
original study had a sample size of 24.

@@

During a trial, four pictures were displayed (target animal, target
instrument, distractor animal, distractor instrument), one in each
corner of the screen, and participants heard an audio prompt that
contained instructions about the action they needed to act out (e.g.,
"Rub the butterfly with the crayon"; see Figure XX)[^1]. Using their
cursor, participants could act out the instructions by clicking on
objects and moving them or motioning over the objects[^2]. After the
action was completed, the participants were instructed to press the
space bar which led to a screen that said "Click Here" in the middle in
order to remove bias in the eye and mouse movements from the previous
trial. The experiment only allowed the participants to move on to the
next trial once the audio was completely done playing and the mouse had
been moved over at least one object.

[^1]: In the original study, the pictures appeared one by one on the
    screen and their names were played as they appeared. We removed this
    introductory portion of the trial to save time

[^2]:  As opposed to the original study we recorded mouse movement
    instead of clicking behavior since not all of the audio prompts
    required clicking. For example, the sentence "locate the camel with
    the straw" may not involve any clicking but rather only mousing over
    the camel.

@@

The images and audios presented to the participants were the same
stimuli used in the original study (available here <link>). The critical
trials were divided into modifier-biased, instrument-biased, and
equibiased conditions, and the filler trials did not contain ambiguous
instructions. Two lists of critical trials were made with different verb
and instrument combinations (e.g., "rub" could be paired with "panda"
and "crayon" in one list and "panda" and "violin" in the second list).
Within each list, the same verb was presented twice but each time with a
different target instrument and animal. The lists were randomly assigned
to the participants to make sure the effects were not caused by the
properties of the animal or instrument images used. The list of verbs
used can be found in Appendix A of the original study.

@@

# Experiment 5

<!-- group e -->

@@

All stimuli, experiment scripts, data, and analysis scripts are
available on the Open Science Framework at <https://osf.io/eubsc/>
(<https://osf.io/eubsc/>). The study pre-registration is available at
<https://osf.io/tv57s> (<https://osf.io/tv57s>).

@@

50 participants for the main task were recruited on Prolific and were
paid \$XX. 8 subjects, 4 from the attractiveness task group and 4 from
the roundness task group, were excluded for incorrect validations.
<!-- they were able to proceed despite bad validation?--> After this
data exclusion, we ended up with 21 participants each for the
attractiveness task and the roundness task. The original sample size in
Shimojo et al. (2003) was 10 participants total. \### Procedure and
Design

@@

During each trial of the main task, two faces were displayed on the two
halves of the screen, one on the left and one on the right (as in Figure
XX). Participants were randomly assigned to one of two tasks:
attractiveness or shape judgment. In the attractiveness task,
participants were asked to chose the more attractice face in the pair
and in the shape judgment task participants were asked to pick the face
that appeared rounder. They pressed the "a" key on their keyboard to
select the face on the left and the "d" key to select the face on the
right. A fixation cross appeared in the center of the screen between
each set of faces. Participants were asked to look at this fixation
cross in order to reset their gaze in between trials (???). The order of
the 19 face pairs was random for each participant.

@@

The faces in our replication were selected from a set of 1,000 faces
within the Flickr-Faces-HQ Dataset. (The face images used in Shimojo et
al. were from the Ekman face database and the AR face database.) These
images were chosen because the person in each image was looking at the
camera with a fairly neutral facial expression and appeared to be over
the age of 18. 27 participants were recruited on Prolific to participate
in stimulus norming (for attractiveness). They were paid \$XX for
completing the experiment. Data from 3 participants was excluded because
their mode response made up more than 50% of their total responses
<!-- is this a cutoff from Shimojo?-->, for a total of 24 participants
in the norming. They each viewed all 172 faces and were asked to rate
them on a scale from 1 (less attractive) to 7 (more attractive) using a
slider. Faces were presented one at a time and in a random order for
each participant. Following Shimojo et al., 19 face pairs were made by
matching two faces that had a difference in mean attractiveness ratings
that was 0.25 points or lower and that matched in gender, race, and age
group (young adult, adult, or older adult).

@@

```{=html}
<!-- posner cueing task
# Experiment 6

@@

## Discussion
 -->
```
# Combined Analyses

@@

```{=html}
<!-- NOTES FROM EMAILS:

@@

We also included a step where if the validation was poor after the first attempt we repeated the calibration and validation procedure one additional time. So some subjects have more validation trials than others. If you look at my R Notebook for group A (just pushed to GH now) you can see some initial attempts to extract validation info and use it to exclude subjects. -->
```
\newpage

@@

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs custom-style="Bibliography"}
:::

```{=tex}
\endgroup
```
